Stochastic Wind Power Forecasting

### 2020-02-09 LaTeX_code/paper/paper_1line.tex
Minor edits
Added MATLAB ReadMe in LaTeX_code

%\author[1]{Waled Alhaddad}
\author[1]{Renzo Caballero}
\author[2]{Ahmed Kebaier}
\author[3]{Marco Scavino}
\author[4]{ Ra\'ul  Tempone}
%\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
\affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
\affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
\affil[3]{Universidad de la Rep\'ublica, Montevideo Uruguay}
\affil[4]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}

@@

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/5.eps}
  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/661.eps}
  \includegraphics[width=60mm,scale=1]{plots/805.eps}
  \caption{Four samples from the Uruguayan data of 2019. Each sample compromises of two 24-hour paths. In blue is an hourly wind power production forecast. In orange is the actual wind power production recorded in 10 minute intervals from  ADME.}
  \label{fig:sample_data}
\end{figure}

>>>>

%\author[1]{Waled Alhaddad}
\author[1]{Renzo Caballero}
\author[2]{Ahmed Kebaier}
\author[3]{Marco Scavino}
\author[4]{ Ra\'ul  Tempone}
%\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
\affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
\affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
\affil[3]{Universidad de la Rep\'ublica, Instituto de Estad\'{\i}stica (IESTA), Montevideo, Uruguay}
\affil[4]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}

@@

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/5.eps}
  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/661.eps}
  \includegraphics[width=60mm,scale=1]{plots/805.eps}
  \caption{Four samples from the Uruguayan data of 2019. Each sample compromises of two 24-hour paths. In blue is an hourly wind power production forecast. In orange is the actual wind power production recorded in 10 minute intervals.}
  \label{fig:sample_data}
\end{figure}
